[dcpo_demsupport] Appendix

### 2020-07-12 paper/dcpo_demsupport_appendix.Rmd
clean up: use vcovBK_se in result_vars_m5; specify plm and mitools pkgs; use here::here; specify col_types for df_controls

```{r claassenWUncertainty}
load("../data/claassen_replication_input.rda")
load("../data/claassen_m5_theta.rda")

ls_year <- 1988:2017
ls_country <- claassen_replication_input$data$country %>% unique

@@

df_controls <- read_csv("../data/Support_democracy_ajps.csv")

df_thetaDraw <- map(df_thetaDraw, function(oneDraw){
  left_join(oneDraw, df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
    pdata.frame(index = c("country", "year"))
})

@@

vcovBK_se <- function(x){
  vcovBK(x, cluster = "time") %>% 
    sqrt(diag(.))}

result_betas_m5 <- MIextract(result_m5, fun = coef)
result_vars_m5 <- MIextract(result_m5, fun = vcovBK_time)

summary(result_m5O)
summary(MIcombine(results = result_betas_m5, 
                  variance = result_vars_m5))
```

>>>>

```{r claassenWUncertainty}
load(here::here("data", "claassen_replication_input.rda"))
load(here::here("data", "claassen_m5_theta.rda"))

ls_year <- 1988:2017
ls_country <- claassen_replication_input$data$country %>% unique()

@@

df_controls <- read_csv(here::here("data", "Support_democracy_ajps.csv"),
                        col_types = cols(
                          .default = col_double(),
                          Country = col_character(),
                          Cnt_code = col_character(),
                          ISO_code = col_character(),
                          Region_UN = col_character()))

df_thetaDraw <- map(df_thetaDraw, function(oneDraw){
  left_join(oneDraw, df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

vcovBK_se <- function(x){
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()}

result_betas_m5 <- mitools::MIextract(result_m5N, fun = coef)
result_vars_m5 <- mitools::MIextract(result_m5N, fun = vcovBK_se)

summary(result_m5O)
summary(mitools::MIcombine(results = result_betas_m5, 
                           variance = result_vars_m5))
```
